It's Never Too Late To Learn\\ \emph{Using Online Machine Learning in Distributed Systems}

### 2016-01-22 writeups/msr_workshop/paper.tex
renamed 'full information' to 'full feedback', and defined what partial feedback means

We propose to use online learning to cope with this complexity. Specifically, we
view a {\em decision} made by a distributed system in the framework of
contextual online learning with partial feedback. This is a natural fit for
distributed systems where: there is plenty of context surrounding each decision,
decisions are made online, and feedback is received only for decisions that were
executed.  Thus, a hand-designed policy in a distributed systems can be replaced
with policy that has been optimized by a contextual learning system. By
supplying rich contexts to this policy, developers capture the complexity of our
environment without having to understand it. Additionally, by optimizing the
policy continuously, the learning system can swiftly adapt to changes in the
environment or service.

Machine learning has certainly been used in the past to optimize system
decisions. Most of this use has been restricted to either offline settings or
expect {\em full information}, whereby a supervised learner is trained on data
that has been annotated with correct labels.
Some systems work in an online setting with full information. An example of that
is a caching layer that uses a learning system to dynamically switch between
existing (hand-designed) cache eviction policies, by running all policies in
parallel and measuring their performance.
Systems that work in an online setting with partial information
tend to be for news or ad recommendation, but examples from systems
infrastructure exist. For example, caching dynamic query content [], tuning
parameters of multicore data structures [], allocating resources to cluster
computing tasks [], and allocating servers to web applications [].  In all of
these systems, the context used to make a decision, and the decision itself, are
{\em local} to a machine. This is achieved by either devising a decentralized
algorithm in the first place, or giving up on global optimality. We are not
aware of any system that makes ``global'' decisions based on truly distributed
architecture or state.

>>>>

We propose to use online learning to cope with this complexity. Specifically, we
view a {\em decision} made by a distributed system in the framework of
contextual online learning with {\em partial feedback} (where the learner only
gets to observe the result of the action it took, rather than all possible
actions). This is a natural fit for distributed systems where: there is plenty
of context surrounding each decision, decisions are made online, and feedback is
received only for decisions that were executed.  Thus, a hand-designed policy in
a distributed systems can be replaced with policy that has been optimized by a
contextual learning system. By supplying rich contexts to this policy,
developers capture the complexity of our environment without having to
understand it. Additionally, by optimizing the policy continuously, the learning
system can swiftly adapt to changes in the environment or service.

%% Hussam: I changed "full information" to "full feedback" to stay consistent
%% with the naming above. Confirmed with Akshay that this is correct terminology

Machine learning has certainly been used in the past to optimize system
decisions. Most of this use has been restricted to either offline settings or
expect {\em full feedback}, whereby a supervised learner is trained on data
that has been annotated with correct labels.
Some systems work in an online setting with full feedback. An example of that
is a caching layer that uses a learning system to dynamically switch between
existing (hand-designed) cache eviction policies, by running all policies in
parallel and measuring their performance.
Systems that work in an online setting with partial feedback
tend to be for news or ad recommendation, but examples from systems
infrastructure exist. For example, caching dynamic query content [], tuning
parameters of multicore data structures [], allocating resources to cluster
computing tasks [], and allocating servers to web applications [].  In all of
these systems, the context used to make a decision, and the decision itself, are
{\em local} to a machine. This is achieved by either devising a decentralized
algorithm in the first place, or giving up on global optimality. We are not
aware of any system that makes ``global'' decisions based on truly distributed
architecture or state.
